Dependent Object Types

### 2012-08-08 article.tex
typo
rev

Proving the DOT calculus type-safe has been an interesting
adventure. We have shown that DOT does not satisfy preservation (also
known as subject-reduction). However, the standard theorems of
preservation and progress are just one way to prove type-safety. We
have sketched a plausible proof of type safety by using the powerful
method of logical relations.

>>>>

Proving the DOT calculus type-safe has been an interesting
adventure. We have shown that DOT does not satisfy preservation (also
known as subject-reduction). However, the standard theorems of
preservation and progress are just one way to prove type safety. We
have sketched a plausible proof of type safety using the powerful
method of logical relations.
